Single-cell virus sequencing of influenza variants that trigger innate immunity

### 2018-09-13 paper/paper.tex
Jesse revisions to qPCR methods

\subsection{qPCR for viral genes and IFN}
\abrcomment{Assuming we use the cycloheximide and ribavirin data as-is, can be modified if not}
For figures \abrcomment{whichever figures} A549 cells were seeded at a density of 10,000 cells/well in a 96-well plate in D10 media 24 hours prior to infection, with four independent wells seeded per experimental treatment. 
Immediately prior to infection D10 media was removed and replaced with influenza growth media and infected with the indicated influenza strains at the indicated MOI.
Viral infections were normalized to an MOI of a previously-characterized relatively-deletion free stock of virus~\citep{russell2018extreme}, with all other strains matched for viral genome copy number as calculated by qPCR, described below.
Crucially, by controlling for genome copy number rather than infectious units we avoid the confounding problem of differing immune stimulation by simply infecting at a higher rate of biologically active but non-infectious particles.
For experimental treatments with ribavirin and cycloheximde, these compounds were added to cells at the time of infection to a final concentration of 100$\mu$M and 50$\mu$g/ml, respectively, both of which are sufficient to block downstream viral replication~\citep{Vanderlinden:2016ec,Reuther:2015ef,Scholtissek:1976wg,killip2014activation}.
At 8 hours post infection media was removed and cell lysates generated using the CellAmp RT-PCR for Direct Prep Kit (Real Time) \& Protein Analysis, following manufacturer's instructions. 
cDNA was synthesized using an oligoDT primer and the SuperScript III first-strand synthesis supermix from ThermoFisher using the manufacturer's protocol. 
Transcript abundance was measured using SYBR green PCR master mix, using a combined anneal/extension step of 60 for one minute with the following primers: HA: 5'-GGCCCAACCACACATTCAAC-3', 5'-GCTCATCACTGCTAGACGGG-3', IFNB1: 5'-AAACTCATGAGCAGTCTGCA-3', 5'-AGGAGATCTTCAGTTTCGGAGG-3', L32: 5'-AGCTCCCAAAAATAGACGCAC-3', 5'-TTCATAGCAGTAGGCACAAAGG-3'.

For titering virus by qPCR, vRNA was harvested from 80 $\mu$l of viral supernatant by the addition of 600 $\mu$l of RLT plus before proceeding with the standard QIAGEN RNeasy Plus Mini kit protocol. 
The cDNA was generated using SuperScript III first-strand synthesis supermix using the manufacturer's protocol, and using the universal vRNA primers of Hoffmann et al. (add Hoffman ref) with the modifications described in Xue et al.\citep{Xue:2017dla}. 
The qPCR was then performed as for mRNA measurements using the HA qPCR primers to measure genome dose.

\jdbcomment{Alistair writes this}

>>>>

\subsection{qPCR for viral genes and IFN}
We performed qPCR for influenza HA (to quantify viral transcription), IFNB1 (to quantify IFN induction), and L32 (a cellular housekeeping gene for normalization).
For the qPCR, we used the SYBR Green PCR Master Mix (Thermo Fisher) according to the manufacturer's protocol.
The qPCR primers were: HA primer 1, 5'-\texttt{GGCCCAACCACACATTCAAC}-3'; HA primer 2, 5'-\texttt{GCTCATCACTGCTAGACGGG}-3'; IFNB1 primer 1, 5'-\texttt{AAACTCATGAGCAGTCTGCA}-3'; IFNB1 primer 2, 5'-\texttt{AGGAGATCTTCAGTTTCGGAGG}-3'; L32 primer 1, 5'-\texttt{AGCTCCCAAAAATAGACGCAC}-3'; L32 primer 2, 5'-\texttt{TTCATAGCAGTAGGCACAAAGG}-3'.

For titering virus by qPCR, vRNA was harvested from 80 $\mu$l of viral supernatant by the addition of 600 $\mu$l of RLT plus before proceeding with the standard QIAGEN RNeasy Plus Mini Kit protocol. 
The cDNA was generated using SuperScript III First-Strand Synthesis SuperMix (Thermo Fisher) using the manufacturer's protocol, and using the universal vRNA primers of \citet{hoffmann2001universal} with the modifications described in \citet{xue2017parallel}. 
The number of HA molecules were then quantified by qPCR to measure genome dose.

\abrcomment{Assuming we use the cycloheximide and ribavirin data as-is, can be modified if not}
For figures \abrcomment{whichever figures} A549 cells were seeded at a density of 10,000 cells/well in a 96-well plate in D10 media 24 hours prior to infection, with four independent wells seeded per experimental treatment. 
Immediately prior to infection D10 media was removed and replaced with influenza growth media and infected with the indicated influenza strains at the indicated MOI.
Viral infections were normalized to an MOI of a previously-characterized relatively-deletion free stock of virus~\citep{russell2018extreme}, with all other strains matched for viral genome copy number as calculated by qPCR, described below.
Crucially, by controlling for genome copy number rather than infectious units we avoid the confounding problem of differing immune stimulation by simply infecting at a higher rate of biologically active but non-infectious particles.
For experimental treatments with ribavirin and cycloheximde, these compounds were added to cells at the time of infection to a final concentration of 100$\mu$M and 50$\mu$g/ml, respectively, both of which are sufficient to block downstream viral replication~\citep{Vanderlinden:2016ec,Reuther:2015ef,Scholtissek:1976wg,killip2014activation}.
At 8 hours post infection media was removed and cell lysates generated using the CellAmp RT-PCR for Direct Prep Kit (Real Time) \& Protein Analysis, following manufacturer's instructions. 
cDNA was synthesized using an oligoDT primer and the SuperScript III first-strand synthesis supermix from ThermoFisher using the manufacturer's protocol.
